Details of specific functions

### 2020-07-13 inst/gitbook/03_specific-tutorials.Rmd
Update 03_specific-tutorials.Rmd

>>>>

### Which disparity metric to choose?

The disparity metric that gives the most consistent results is the following one:

```{r}
best.metric <- function() return(42)
```
Joke aside, this is a legitimate question that has no simple answer: **it depends on the dataset and question at hand**.
Thoughts on which metric to choose can be find in @moms and @Guillerme2020 but again, will ultimately depend on the question and dataset.
The question should help figuring out which type of metric is desired: for example, in the question "does the extinction released niches for mammals to evolve", the metric in interest should probably pick up a change in size in the trait space (the release could result in some expansion of the mammalian morphospace); or if the question is "does group X compete with group Y", maybe the metric of interested should pick up changes in position (group X can be displaced by group Y).

In order to visualise what signal different disparity metrics are picking, you can use the [`moms`](https://tguillerme.shinyapps.io/moms/) that come with a detailed [manual](https://rawcdn.githack.com/TGuillerme/moms/master/inst/moms_vignette.html) on how to use it.

Alternatively, you can use the `test.metric` function:

#### `test.metric`

This function allows to test whether a metric picks different changes in disparity. It intakes the space on which to test the metric, the disparity metric and the type of changes to apply gradually to the space.
Basically this is a type of biased data rarefaction (or non-biased for `"random"`) to see how the metric reacts to specific changes in trait space.

```{r}
# Creating a 2D uniform space
example_space <- space.maker(300, 2, runif)

## Testing the product of ranges metric on the example space
example_test <- test.metric(example_space, metric = c(prod, ranges),
                           shifts = c("random", "size")) 
```

By default, the test runs three replicates of space reduction as described in @moms by gradually removing 10% of the data points following the different algorithms from @moms (here the `"random"` reduction and the `"size"`) reduction, resulting in a `dispRity` object that can be summarised or plotted.
The number of replicates can be changed using the `replicates` option.
Still by default, the function then runs a linear model on the simulated data to measure some potential trend in the changes in disparity. 
The model can be changed using the `model` option.
Finally, the function runs 10 reductions by default from keeping 10% of the data (removing 90%) and way up to keeping 100% of the data (removing 0%).
This can be changed using the `steps` option.
A good disparity metric for your dataset will typically have no trend in the `"random"` reduction (the metric is ideally not affected by sample size) but should have a trend for the reduction of interest.

```{r}
## The results as a dispRity object
example_test

## Summarising these results
summary(example_test)

## Or visualising them
plot(example_test)
```
